Storing messages with multipartite neural cliques

### 2014-06-29 Articles/article.tex
...

	\begin{figure}
		\includegraphics[width=8.5cm]{comparaison_regles_pool5_a2c4l512e2}
		\caption{2 activities per cluster, 4 clusters, 512 neurons per cluster, two erasures, each point is the mean of 5 networks with 1000 sampled messagges, analytical result in continuous black}
		\end{figure}

	\begin{figure}
		\includegraphics[width=8.5cm]{comp_erreurs_a2l512c4er1}
		\caption{2 activities per cluster, 4 clusters, 512 neurons per cluster, two erasures, each point is the mean of 5 networks with 1000 sampled messagges, analytical result in continuous black}
	\end{figure}

@@

	$P(n_{ge} = a(c - c_e) + \gamma + x) = {a c_e - 1 \choose x} d^x (1-d)^{a c_e-1-x}$

>>>>

	\begin{figure}
		\includegraphics[width=8.5cm]{comparaison_regles_pool5_a2c4l512e2}
		\caption{2 activities per cluster, 4 clusters, 512 neurons per cluster, two erasures, each point is the mean of 5 networks with 1000 sampled messages, analytical result in continuous black}
		\end{figure}

	\begin{figure}
		\includegraphics[width=8.5cm]{remplacement_figure3g1}
		\caption{2 activities per cluster, 4 clusters, 512 neurons per cluster, one erroneous cluster, each point is the mean of 5 networks with 1000 sampled messages, analytical result in continuous black}
	\end{figure}

@@

	$P(n_{ge} = a(c - c_e) + x) = {a (c_e - 1) \choose x} d^x (1-d)^{a (c_e - 1)-x}$
